報告

### 2018-03-20 DiagrammeR/slide.Rmd
update

---
title: "報告"
subtitle: "副標題"
author: Yongfu Liao
date: March 13, 2018
output:
  ioslides_presentation:
    fig_height: 3
    css: ../style_sheets/presentation_style.css
    incremental: false
    logo: tux.svg
    df_print: kable
---

@@

## 中文

@@

>>>>

---
title: "報告"
subtitle: "副標題"
author: Yongfu Liao
date: March 13, 2018
output:
  ioslides_presentation:
    fig_height: 3
    css: ../style_sheets/presentation_style.css
    incremental: true
    transition: 0.4
    logo: tux.svg
    df_print: kable
---

@@

Part 1
==================

## 中文 {.build}

@@

Part 2
==================
